---
title: "physical-risk-methodology"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{physical-risk-methodology}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
suppressPackageStartupMessages(library(dplyr))
library(r2dii.physical.risk)
```

This article documents the methodology used in this repository to estimate the
risk a financial portfolio incurs as a result of changing physical hazards,
caused by climate change. The article assumes a basic understanding of
PACTA.

# Physical Risk

Climate change poses a financial risk from several different angles. Transition
risk is associated with the economic transition from high- to low-carbon
technologies. If the transition is unmediated, it could cause a shock to the
financial system. Litigation risk is the risk associated with potential lawsuits
against companies that contribute significantly to climate change. Finally,
physical risk, is associated with the real physical risk that climate hazards
pose to assets. 

Physical risks can be classified as either acute or chronic. 
- An example of an acute physical risk might be the risk of increased flood
frequency on real estate
- For chronic risks, you might imagine how the consistent increase in
temperature, or precipitation, might affect agriculture

As you can imagine, there are many different potential physical hazards that
arise from climate change.

## Canonical Risk Formulation

Physical risk can be expressed using the canonical risk formulation (below): 

$$ Risk = Hazard * Exposure * Vulnerability $$
where: 

- $Hazard$ quantifies the physical hazard itself (e.g. increase in river flood
depth) 
- $Exposure$ quantifies how many assets are actually exposed to the $Hazard$
(e.g which many physical are located in areas with increased risk to river
flood)
- $Vulnerability$ quantifies how much the $Hazard$ may damage the exposed assets
(sometimes described as "damage functions")

Crucially, our model currently lacks "damage functions". This methodology spans
only the $Hazard$ and $Exposure$ estimations.

# Methodology

Now, let's go over the physical risk methodology presented in this repository. 

## Data

First, we will give a brief overview of the crucial datasets used in this 
methodology. 

## Input Portfolio

A typical "input portfolio" might look something like this: 

``` {r}
portfolio <- tribble(
  ~isin, ~market_value, ~currency,
  "JP3868400007",       50000L,     "GBP",
  "FR0000571218",       28136L,     "GBP",
  "FR0011883966",      117291L,     "GBP"
)

portfolio

```

The input portfolio that is actually used in this physical risk assessment is
already slightly pre-processed. The file used is the `total_portfolio.rda` file
that can be found in the folder `30_Processed_Inputs` of a typical PACTA
project. What this means is that it has already been extended using financial
data, and contains some columns that are not present in the above dataset.
Crucially, it contains the following columns:

``` {r}
portfolio <- tribble(
  ~portfolio_name,    ~company_name, ~company_id, ~corporate_bond_ticker,          ~isin, ~holding_id, ~asset_type, ~security_mapped_sector, ~value_usd,
  "some portfolio", "a power company",          "C1",                  "ABC", "AB1234567890",        123L,    "Equity",                 "Power",     45000L
)

portfolio
```

## Financial Data
Further financial data is used to understand the company ownership structure of 
any company in the portfolio. The goal is to be able to link each company that 
is present in the portfolio, all the way down to the individual physical assets 
that it might own and operate. 

First, we need to understand which companies own the individual asset:

``` {r}
asset_level_owners <- tribble(
  ~company_id,        ~asset_id, ~ownership_share,
  "C2",    "A1",              25,
  "C3",    "A1",              25,
  "C4",  "A1",                50
)

asset_level_owners

```

In this case, we see that the power plant with ID `"A1"` is jointly owned by 
companies with IDs `c("C1", "C2", "C3")`. 

However, the only company in the portfolio (above) has the ID `"C5"`? We will 
see below that this company owns a stake of the above company. 

To understand this, we need a dataset indicating the corporate ownership 
structure of each physical asset-owning company. This dataset looks something 
like this: 

``` {r}
company_ownership_tree <- tribble(
  ~company_id, ~subsidiary_id, ~linking_stake, ~ownership_level,
          "C1",         "C2",             100,                 2,
          "C2",         "C2",             100,                1,
          "C3",         "C3",             100,                1,
          "C4",         "C5",             100,                1
  )

company_ownership_tree
```


## Physical Assets

The physical asset data used looks something like this: 

```{r}
ald <- tribble(
  ~asset_name, ~asset_location, ~latitude, ~longitude, ~sector,     ~technology, ~year, ~economic_unit, ~economic_output, ~asset_id,
  "Some Wind Farm",            "ES",       42L,        -3L, "Power", "RenewablesCap", 2020L,           "MW",             400L,      "A1",
  "Some Wind Farm",            "ES",       42L,        -3L, "Power", "RenewablesCap", 2021L,           "MW",             420L,      "A1",
  "Some Wind Farm",            "ES",       42L,        -3L, "Power", "RenewablesCap", 2022L,           "MW",             440L,      "A1"
)

ald
```

This data contains physical assets, including geographic latitude and longitude
coordinates, for a variety of sectors, as well as production or capacity values 
for each asset. 

## Climate Hazard Scenarios 
### Climate Analytics

Climate data is "pre-processed", and harmonized with the physical asset data. 
For each combination of asset, scenario, model, period and hazard, there is an 
associated `relative_change` value. This value represents the estimated relative 
difference in the hazard (e.g. expected preciptation):

```{r}
climate_data <- tibble::tribble(
  ~asset_name, ~scenario,     ~model, ~period,    ~hazard, ~relative_change, ~asset_id,
  "Some Wind Farm",   "rcp26", "Ensemble",   2100L, "prAdjust",            0.004,      "A1",
  "Some Wind Farm",   "rcp45", "Ensemble",   2100L, "prAdjust",             0.03,      "A1",
  "Some Wind Farm",   "rcp60", "Ensemble",   2100L, "prAdjust",             0.04,      "A1"
)

climate_data
```

# Methodology

Now let's explain the methodology, by using the above datasets directly. 

First, we expand each company in the portfolio by all of it's subsidiary 
companies. Companies with no matching data will be dropped.

``` {r}
out <- portfolio %>% 
  inner_join(company_ownership_tree, by = "company_id") %>% # join ownership
  inner_join(asset_level_owners, by = c(subsidiary_id = "company_id")) %>% # join asset owners
  inner_join(ald, by = "asset_id")
```

We then allocate an amount of economic output proportional to the ownership of
the asset, to the portfolio:

``` {r}
out <- out %>% 
  mutate(portfolio_economic_value = (linking_stake/100) * (ownership_share/100) * economic_output)

  select(
    out,
    company_name, 
    value_usd, 
    asset_location, 
    latitude, 
    longitude, 
    sector, 
    technology, 
    year, 
    economic_unit, 
    portfolio_economic_value
    )
```

With the portoflio now linked to it's physical assets, and some proportional 
amount of production connected to each asset linked to the portfolio, we can 
begin to connect the climate hazards. 

Since the hazards' geographic locations have already been harmonized to the 
asset locations, we simply match each asset to the portfolio by `asset_id`: 

``` {r}
out <- out %>% 
  inner_join(climate_data, by = "asset_id") %>% 
    select(
    company_name, 
    value_usd, 
    asset_location, 
    latitude, 
    longitude, 
    sector, 
    technology, 
    year, 
    economic_unit, 
    portfolio_economic_value,
    scenario, 
    model, 
    period, 
    hazard,
    relative_change
    )

out <- out %>% 
  group_by(sector) %>% 
  mutate(portfolio_economic_value_share_sector = portfolio_economic_value/sum(portfolio_economic_value)) %>% 
  ungroup()

provider <- "Fake Data Provider"
scenario <- "rcp26"
hazard <- unique(out$hazard)
model <- unique(out$model)
period <- unique(out$period)

r2dii.physical.risk:::plot_sector_absolute_portfolio_economic_value(
  out, 
  provider_sub = "Climate Data", 
  scenario_sub = scenario,
  hazard_sub = hazard,
  model_sub = model,
  period_sub = period
    )
```
